% !TeX root = main.tex

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

          % \resumeProjectHeading
          % {\textbf{Iota Technologies} $|$ \footnotesize\emph{Shopify}\vspace{8pt}}{April 2022 -- October 2023}
          %   \begin{itemize}
          %       \item 
          %       Redesigned a shopify website to ensure smooth functioning and a modern design.  
          %       \item 
          %       Produced a 200\% increase in organic traffic. 
          %       \item 
          %       Created processes to support inventory management between various ecommerce platforms. 
          %     \end{itemize}
          \resumeProjectHeading
          {\textbf{Jacqueline Construction}\vspace{8pt} $|$ \footnotesize\emph{Software Developer - Typescript/Node/NextJS/Express}}{October 2024 -- Current}
            \begin{itemize}
              \item 
              Developed a full-stack job tracking application that reduced project reporting time by 70\%. 
              \item 
              Collaborated with Upper Management and Site Supervisors to ensure seamless user experience, increasing adoption rate by 40\% among site supervisors.
              \item 
              Automated toll tracking with NTTA API integrations to generate  automated driver-level reports 
              \item
              Deployed a time tracker for billable hours by project to support accurate P\&L generation.         
              \end{itemize}
              \resumeProjectHeading
              {\textbf{QLU.AI}\vspace{8pt} $|$ \footnotesize\emph{FullStack Engineer – TypeScript, Node.js, Next.js, Express}}{June 2024 -- October 2024}
              \begin{itemize}
                \item Developed a high-performance, Cassandra-backed search algorithm, improving query speed by 50\% while ensuring end-to-end data encryption.
                \item Engineered and deployed a scalable attachment system processing over 10,000 files daily, optimizing file handling for clients.
                \item Partnered with designers and product stakeholders to revamp core user flows, leading to a 20\% increase in user engagement.
              \end{itemize}
              \resumeProjectHeading
              {\textbf{Systems Limited}\vspace{8pt} $|$ \footnotesize\emph{Backend Development Intern – Java, Springboot, JBDC}}{June 2024 -- October 2024}
              \begin{itemize}
                \item Designed and developed an end-to-end internal ticket tracking system with two service variants using SOAP and REST APIs.
                \item Built backend services using Node.js and Express, exposing both SOAP and REST endpoints, and implemented business logic via modular servlets and microservices.
                \item Developed a mock frontend with Next.js to simulate user interactions and visualize ticket data for internal QA and stakeholder demos.
              \end{itemize}


          % \resumeProjectHeading
          % {\textbf{Copywriter} $|$ \footnotesize\emph{Multiple Clients}\vspace{8pt}}{August 2018 -- Present}
          % {\small{}}
          % \begin{itemize}
          %     \item
          %     Acted as Lead Copy Writer for USbased fitness apparel company SizeUp Apparel.
          %     \item 
          %     Overhauled the catalogue copy for over 100+ products.
          %     \item
          %      Coming Up with exciting, engaging copy, and eye grabbing content to convert those leads to sales. (Freelance)
          % \end{itemize}

    \resumeSubHeadingListEnd